### 2019-05-28 dantzig_selector/report/3_theorems_and_proofs.tex
Create ConTeXt slides

Let us call it a day and set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l >0}.
They are (with a slight of abuse of meaning of \m {\o_t} and so on)
\Disp{
\NC d \o_t
=\NC \F {1} {\R {\pi} \l} \exp
  \RB {-\F{1}{\l^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
\NC d \o_t
=\NC \F {1} {\R {\pi} \l} \exp
  \RB {-\F{1}{\l^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
\NC n_R
= \NC 0, 1, 2, \dots, N_R -1 \NR
\NC n_Y
= \NC 0, 1, 2, \dots, N_Y -1 \NR
}

@@

Start with the observtion
\Result
{Lemma}
{
\Disp {
\NC \NC \MB{E} \SB {\M{P} \DB {n_y, n_h} \M{P} \DB {n_y', n_h'}} \NR
\NC = \NC \startcases
\l_R^4 \l_B^4, \Q \MC n_y =n_y', n_h =n_h' \NR
0, \Q \NC \Rm {otherwise} \NR
\stopcases \NR
}
}

Notice
\Disp {
\NC \M{P} ^\Adj \M{P}
=\NC
\RB {
   \RB {\M{K} ^\Tr \M {F}_R^\ast \M {F}_B^\ast}
   \otimes \RB {\M {K} \M {W}_R \M {W}_B}
}
\RB {
   \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast}
   \otimes \RB {\M {W}_B \M {W}_R \M {K}}
} \NR
\NC =\NC
\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast \M{K}^\Tr \M {F}_R^\ast \M {F}_B^\ast}
\otimes \RB {\M {W}_B \M {W}_R \M{K} \M{K}^\Adj \M {W}_R^\Adj \M {W}_B^\Adj} \NR
\NC =\NC
\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M {F}_R^\ast \M {F}_B^\ast}
\otimes \RB {\M {W}_B \M {W}_R \M {W}_R^\Adj \M {W}_B^\Adj} \NR[+]
}
where, restating (), \m {\M {Q} :=\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R}}.

@@

To make expressions more compact, introduce
\Disp {
\NC \i_2 \SB {x_0, x_1}
=\NC \startcases
\NC 1, \MC \Q x_0 =x_1 \NR
\NC 0, \NC \Q \Rm {otherwise} \NR
\stopcases \NR
\NC \i_4 \SB {x_0, x_1, x_2, x_3}
=\NC \startcases
\NC 1, \MC \Q x_0 =x_1 =x_2 =x_3 \NR
\NC 0, \NC \Q \Rm {otherwise} \NR
\stopcases \NR
}
And, for any permutation \m {\s} on \m {\CB {1, 2, 3, 4}},
\Disp {
\NC \i_{2,2} \SB {x_0, x_1, x_2, x_3}
=\NC \startcases
\NC 1, \MC \Q x_{\s \RB{0}} =x_{\s \RB{1}} \neq x_{\s \RB{2}} =x_{\s \RB{3}} \NR
\NC 0, \NC \Q \Rm {otherwise} \NR
\stopcases \NR
}

\Result
{Lemma}
{
\Disp {
\NC \NC \MB{E} \SB {\RB {\M{F}_R \M{F}_B} \DB {n_H, n_Y} \RB {\M{F}_R \M{F}_B} \DB {n_H', n_Y'}} \NR
\NC = \NC \MB{E} \SB {\RB {\M{W}_R \M{W}_B} \DB {n_Y, n_H} \RB {\M{W}_R \M{W}_B} \DB {n_Y', n_H'}} \NR
\NC = \NC N_R \D \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D \RB {\l_R^2 +\l_B^2} \NR
}
}

To see this, expanding the definition
\Disp {
\NC \NC \RB {\M{W}_B ^\Adj \M{W}_R ^\Adj} \DB {n_Y, n_H} \RB {\M{F}_R \M{F}_B} \DB {n_Y', n_H'} \NR
\NC =\NC
\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H, n_R} \M{F}_B \DB {n_R, n_Y}}
\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H', n_R} \M{F}_B \DB {n_R, n_Y'}} \NR
}
When either \m {n_y \neq n_y'} or \m {n_h \neq n_h'}, no term is an all-square product.
After taking expectation, the expectation sign is distributed, and every term vanishes.
But when \m {n_y =n_y'} or \m {n_h =n_h'}, the only terms that remains are
\Disp {
\NC \NC \sum_{n_R=0}^{N_R-1}
\MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2}
\MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
\NC = \NC N_R \D \RB {M_{R,2} +M_{B,2}} \NR
}

@@

Fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we shall study the probability concentration of \m {\VNm {\M{F}_B \V{u}}_2^2} and \m {\VNm {\M{F}_B \V{u}}_2^4}.
The two moments are present in Chebyshev bound.
\Disp{
\NC \NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2} \NR
\NC = \NC \MB{E} \SB {
  \sum_{n_y=0}^{N_y-1}
  \Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2
} \NR
\NC = \NC \sum_{n_y=0}^{N_y-1}
  \MB{E} \SB {\Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2}
\NR
\NC = \NC
\sum_{n_y=0}^{N_y-1}
  \MB{E} \SB {
     2 \sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
       \MF {Re} \SB{
         \M{Q} \DB {n_y, n_h} ^\ast \M{Q} \DB {n_y, n_h'}
         \V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
       }
   } \NR
\NC \NC \Q \Q +\sum_{n_y=0}^{N_y-1}
  \MB{E}
     \SB {\sum_{n_h=0}^{N_h-1} \Nm {\M{Q} \DB {n_y, n_h}}^2 \Nm {\V{u} \DB{n_h}}^2}
\NR
\NC = \NC
2 \sum_{n_y=0}^{N_y-1}
\sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
\MF {Re} \SB{
   \MB{E} \SB {\M{Q} \DB {n_y, n_h}^\ast}
   \MB{E} \SB {\M{Q} \DB {n_y, n_h'}}
}
\V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
\NR
\NC \NC \Q \Q +\sum_{n_y=0}^{N_y-1}
   \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
\NR
\NC = \NC N_y \D N_R^2 \l_B^4 \l_R^4  \D \VNm {\V{u}} _2 ^2 \NR[+]
}
Thus, we may set
\Disp{
\NC \l_B
=\NC \l_R \NR
\NC =\NC \F {1} {\R {N_Y N_R}} \NR[+]
}
To make
\Disp{
\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2}
=\NC \VNm {\V{u}} _2 ^2
}

Similarly, we have to find, in advance, the second moment.
\Disp{
\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^4}
=\NC \MB{E} \SB {
  \RB {
    \sum_{n_R=0}^{N_R-1}
    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{Q} \DB {n_R, n_Y} ^\ast \V{u} \DB{n_Y}} ^2
  } ^2
} \NR
\NC = \NC E_1 +E_2 +E_3 +E_4 +E_5 \NR[+]
}
These terms are discussed as immediately follows.
Without spelling out everything, we notice that as long as a term has a single \m {\M{Q} \DB {n_R, n_Y}} factor, it's expectation is zero.
The terms that does not vanish is a product of three numbers: How many terms, the moment involving \m {\M{Q} \DB {n_y, n_h}}, the norm of \m {\V{u}}.
We will repeatedly bound \m {N_R \D (N_R-1) /2} by \m {N_R^2 /2}, and bound \m {\Nm {\V{u}} _2} by \m {\Nm {\V{u}} _2}, and so on.
\Disp {
\NC E_1
=\NC \sum_{n_y=0}^{N_y-1} \sum_{n_h=0}^{N_h-1}
\Nm {\M{Q} \DB {n_y, n_h}} ^4
\Nm {\V{u} \DB{n_h}} ^4 \NR
\NC =\NC N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \D \Nm {\V{u}} _4 ^4 \NR
\NC \leq \NC 4 N_Y ^{-2} N_R ^{-2} \Nm {\V{u}} _2 ^4 \NR[+]
}
\Disp {
\NC E_2
= \NC \sum _{\Stack { n_y, n_y' =0 \NR n_y <n_y' }}^{N_y-1}
\sum _{n_h =0}^{N_h-1}
\Nm {\M{Q} \DB {n_y, n_h}} ^2
\Nm {\M{Q} \DB {n_y', n_h}} ^2
\Nm {\V{u} \DB{n_h}} ^4 \NR
\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D 8 N_R ^{-2} N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
\NC \NC \Q \Q + \F{1}{2} N_Y \RB{N_Y-1} \D N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \VNm {\V{u}} _2 ^4 \NR
\NC \leq \NC 4 N_R ^{-2} \VNm {\V{u}} _2 ^4 \NR[+]
}
\Disp {
\NC E_3
=\NC \sum _{n_y, n_y' =0}^{N_y-1}
\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
\Nm {\M{Q} \DB {n_y, n_h}} ^2
\Nm {\M{Q} \DB {n_y', n_h'}} ^2
\Nm {\V{u} \DB{n_h}} ^2
\Nm {\V{u} \DB{n_h'}} ^2 \NR
\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D 8 N_R ^{-2} N_Y ^{-4} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC \leq \NC 4 N_R ^{-2} N_Y ^{-1} \VNm {\V{u}} _2 ^4 \NR[+]
}
\Disp {
\NC E_4
=\NC \sum _{n_y =0}^{N_y-1}
\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
\Nm {\M{Q} \DB {n_y, n_h}} ^2
\Nm {\M{Q} \DB {n_y, n_h'}} ^2
\Nm {\V{u} \DB{n_h}} ^2
\Nm {\V{u} \DB{n_h'}} ^2 \NR
\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D 8 N_R ^{-2} N_Y ^{-4} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC \leq \NC 4 N_H ^2 N_R ^{-2} N_Y ^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
}
The last one is more difficult.
In the end we used Muirhead inequality to get \m {\i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'} \V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \leq \RB {1/6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4}}.
\Disp {
\NC E_5
\NC = \sum _{
    \Stack {
      0 =n_h <n_h' \NR
      0 =m_h <m_h' \NR
      n_h +m_h' =n_h' +m_h \NR
      \Fl {n_h/N_H} =\Fl {n_h'/N_H} \NR
      \Fl {m_h/N_H} =\Fl {m_h'/N_H}
    }
  } ^{N_H-1}
  \sum _{\Stack { 0 =n_y <n_y' \NR \Fl {n_y/N_Y} =\Fl {n_y'/N_Y} }} ^{N_y-1} \NR
  \NC \NC \Q \Q \Q \Q
  \Nm {\M{Q} \DB {n_y, n_h}}
  \Nm {\M{Q} \DB {n_y, n_h'}}
  \Nm {\M{Q} \DB {n_y, m_h}}
  \Nm {\M{Q} \DB {n_y, m_h'}} \NR
  \NC \NC \Q \Q \Q \Q
  \VNm {\V{u} \DB{n_h}} ^2
  \VNm {\V{u} \DB{n_h'}} ^2
  \VNm {\V{u} \DB{m_h}} ^2
  \VNm {\V{u} \DB{m_h'}} ^2 \NR
\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \NR
\NC \NC \Q \Q \Q \Q
\D 8 N_R ^{-2} N_Y ^{-4} \NR
\NC \NC \Q \Q \Q \Q
\D \sum_{\Stack {n_h, n_h' =0}} ^{N_H-1}
\sum_{\Stack {m_h, m_h' =0}} ^{N_H-1}
\i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'} \NR
\NC \NC \Q \Q \Q \Q
\VNm {\V{u} \DB{n_h}} \VNm {\V{u} \DB{n_h'}}
\VNm {\V{u} \DB{m_h}} \VNm {\V{u} \DB{m_h'}} \NR
\NC \leq \NC \F{1}{3} N_Y ^{-1} N_H ^4 N_R ^{-2} \VNm {\V{u}} _2 ^4. \NR[+]
}

@@

\Result
{Definition}
{
Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
Let bijection \m {\s: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
\Disp{
\NC \V{v} \DB {\s \SB {n}}
\leq \NC \V{v} \DB {\s \SB {n-1}} \NR[+]
\NC n =\NC 1, \dots, N_p-1 \NR
}
Its existence is evident.

@@

\Result
{Lemma}
{
\Disp {
\NC \Nm {\IP { \V {z} \SB {\o_z}, \M {P} \DB {:, n_g} }}
\leq \NC  2 \R {\log N_h} \NR
\NC n_g 
=\NC 1, \dots, N_h. \NR
}
with probability \m {\geq 1 -N_h}.
}

@@

\Result
{Lemma}
{
With the condition that \m {\M {P}} satisfies RIP for \m {\d_s \SB {\M{P}}},
\Disp {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC  4 \R {\log N_h} \NR
\NC n_g 
=\NC 1, \dots, N_h. \NR
}
with probability \m {\geq 1 -N_h}.
}

>>>>

Let us call it a day and set each entry of \m {\M{F}_B} to be i.i.d.\ Gaussian r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l >0}.
They are (with a slight of abuse of meaning of \m {\o_t} and so on)
\Disp{
\NC d \o_t
=\NC \F {1} {\R {\pi} \l} \exp
  \RB {-\F{1}{\l^2} \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
d \MF{Re} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
\NC d \o_t
=\NC \F {1} {\R {\pi} \l} \exp
  \RB {-\F{1}{\l^2} \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} ^2}
d \MF{Im} \SB {\M{F}_B \DB {n_R, n_Y}} \NR[+]
\NC n_R
= \NC 0, 1, 2, \ldots, N_R -1 \NR
\NC n_Y
= \NC 0, 1, 2, \ldots, N_Y -1 \NR
}

@@

Observe
\Disp {
\NC \M{P} ^\Adj \M{P}
=\NC
\RB {
   \RB {\M{K} ^\Tr \M {F}_R^\ast \M {F}_B^\ast}
   \otimes \RB {\M {K} \M {W}_R \M {W}_B}
}
\RB {
   \RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast}
   \otimes \RB {\M {W}_B \M {W}_R \M {K}}
} \NR
\NC =\NC
\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M{K}^\ast \M{K}^\Tr \M {F}_R^\ast \M {F}_B^\ast}
\otimes \RB {\M {W}_B \M {W}_R \M{K} \M{K}^\Adj \M {W}_R^\Adj \M {W}_B^\Adj} \NR
\NC =\NC
\RB {\M {F}_B^\Tr \M {F}_R^\Tr \M {F}_R^\ast \M {F}_B^\ast}
\otimes \RB {\M {W}_B \M {W}_R \M {W}_R^\Adj \M {W}_B^\Adj}
\RB {\M {F}_R^\Tr \M {F}_B^\Tr} \otimes \RB {\M {W}_B \M {W}_R} \NR
\NC := \NC \M{Q} \NR[+]
}

@@

\Result
{Definition}
{
To make expressions more compact, introduce the indication function \m {\i}, so that, for some injective \m {\s:\; \CB {0, \ldots, M-1} \CB {0, \ldots, N-1}},
\Disp {
\NC \i_{a_0, \ldots, a_{M-1}} \SB {x_0, \ldots, x_{N-1}}
=\NC \startcases
\NC 1, \MC \Q \exists \s:\; x_0 \cdots x_{N-1}
=x_{\s \SB {0}} ^{a_0} \cdots x_{\s \SB {M-1}} ^{a_{M-1}} \NR
\NC 0, \NC \Q \Rm {otherwise} \NR
\stopcases \NR
}
}

For short, denote
\Disp {
\NC F :=\NC \M {F}_B \M {F}_R \NR
\NC W :=\NC \M {W}_R \M {W}_B \NR
}
\Result
{Lemma}
{
\Disp {
\NC \NC \MB{E} \SB {\M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'}} \NR
\NC = \NC \MB{E} \SB {\M{W}^\Adj \DB {n_Y, n_H} \M{W}^\Adj \DB {n_Y', n_H'}} \NR
\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR
}
}

To see this, expanding the definition
\Disp {
\NC \NC \M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'} \NR
\NC =\NC
\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H, n_R} \M{F}_B \DB {n_R, n_Y}}
\RB {\sum_{n_R=0}^{N_R-1} \M{F}_R \DB {n_H', n_R} \M{F}_B \DB {n_R, n_Y'}} \NR
}
Examine the \m {\i_{1,1} \SB {n_H, n_H'}} factor and \m {\i_{1,1} \SB {n_Y, n_Y'}} factors.
After taking expectation, the expectation sign is distributed, and every term vanishes.
Other terms that remains are \m {\i_{2} \SB {n_H, n_H'}} and \m {\i_{2} \SB {n_Y, n_Y'}}, namely
\Disp {
\NC \NC \sum_{n_R=0}^{N_R-1}
\MB{E} \SB {\M{F}_R \DB {n_H, n_R}^2}
\MB{E} \SB {\M{F}_B \DB {n_R, n_Y}^2} \NR
\NC = \NC N_R \D M_{R,2} M_{B,2} \NR
}

By the same token,
\Result
{Lemma}
{
\Disp {
\NC \NC \MB{E} \SB {\M{F} \DB {n_H, n_Y} \M{F} \DB {n_H', n_Y'} \M{F} \DB {n_H, n_Y} \M{F} \DB {n_H, n_Y}} \NR
\NC = \NC \MB{E} \SB {\RB {\M{W}_B ^\Adj \M{W}_R ^\Adj} \DB {n_Y, n_H} \RB {\M{W}_B ^\Adj \M{W}_R ^\Adj} \DB {n_Y', n_H'}} \NR
\NC = \NC \i_2 \SB {n_H, n_H'} \D \i_2 \SB {n_Y, n_Y'} \D N_R \l_R^2 \l_B^2 \NR
}
}

@@

\Result
{Lemma}
{
\Disp {
\NC \NC \MB{E} \SB {\M{Q} \DB {n_Y, n_H} \M{Q} \DB {n_Y', n_H'}} \NR
\NC = \NC \startcases
N_R^2 \l_R^4 \l_B^4, \Q \MC n_Y =n_Y', n_H =n_H' \NR
0, \Q \NC \Rm {otherwise} \NR
\stopcases \NR
}
}

Now, fix any test vector \m {\V{u} \in \MB{V}_\MB{C} \SB{N_Y}}, we shall study the probability concentration of \m {\VNm {\M{F}_B \V{u}}_2^2} and \m {\VNm {\M{F}_B \V{u}}_2^4}.
The two moments are present in Chebyshev bound.
\Disp{
\NC \NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2} \NR
\NC = \NC \MB{E} \SB {
  \sum_{n_y=0}^{N_y-1}
  \Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2
} \NR
\NC = \NC \sum_{n_y=0}^{N_y-1}
  \MB{E} \SB {\Nm {\sum_{n_h=0}^{N_h-1} \M{Q} \DB {n_y, n_h} ^\ast \V{u} \DB{n_h}} ^2}
\NR
\NC = \NC
\sum_{n_y=0}^{N_y-1}
  \MB{E} \SB {
     2 \sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
       \MF {Re} \SB{
         \M{Q} \DB {n_y, n_h} ^\ast \M{Q} \DB {n_y, n_h'}
         \V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
       }
   } \NR
\NC \NC \Q \Q +\sum_{n_y=0}^{N_y-1}
  \MB{E}
     \SB {\sum_{n_h=0}^{N_h-1} \Nm {\M{Q} \DB {n_y, n_h}}^2 \Nm {\V{u} \DB{n_h}}^2}
\NR
\NC = \NC
2 \sum_{n_y=0}^{N_y-1}
\sum_{\Stack { n_h, n_h'=0 \NR n_h <n_h' }}^{N_h-1}
\MF {Re} \SB{
   \MB{E} \SB {\M{Q} \DB {n_y, n_h}^\ast}
   \MB{E} \SB {\M{Q} \DB {n_y, n_h'}}
}
\V{u} \DB{n_h} \V{u} \DB{n_h'} ^\ast
\NR
\NC \NC \Q \Q +\sum_{n_y=0}^{N_y-1}
   \sum_{n_h=0}^{N_h-1} \MB{E} \SB {\Nm {\M{Q} \DB {n_y, n_h}}^2} \Nm {\V{u} \DB{n_h}}^2
\NR
\NC = \NC N_y \D N_R^2 \l_B^4 \l_R^4  \D \VNm {\V{u}} _2 ^2 \NR[+]
}
Thus, we may set
\Disp{
\NC \l_B
=\NC \l_R \NR
\NC =\NC \F {1} {\R {N_Y N_R}} \NR[+]
}
To make
\Disp{
\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^2}
=\NC \VNm {\V{u}} _2 ^2
}

Similarly, we have to find, in advance, the second moment.
\Disp{
\NC \MB{E} \SB {\VNm {\M{Q} \SB {\o_t, \o_r} \V{u}} _2 ^4}
=\NC \MB{E} \SB {
  \RB {
    \sum_{n_R=0}^{N_R-1}
    \Nm {\sum_{n_Y=0}^{N_Y-1} \M{Q} \DB {n_R, n_Y} ^\ast \V{u} \DB{n_Y}} ^2
  } ^2
} \NR
\NC = \NC E_1 +E_2 +E_3 +E_4 +E_5 \NR[+]
}
These terms are discussed as immediately follows.
Without spelling out everything, we notice that as long as a term has a single \m {\M{Q} \DB {n_R, n_Y}} factor, it's expectation is zero.
The terms that does not vanish is a product of three numbers: How many terms, the moment involving \m {\M{Q} \DB {n_y, n_h}}, the norm of \m {\V{u}}.
We will repeatedly bound \m {N_R \D (N_R-1) /2} by \m {N_R^2 /2}, and bound \m {\Nm {\V{u}} _2} by \m {\Nm {\V{u}} _2}, and so on.
\Disp {
\NC E_1
=\NC \sum_{n_y=0}^{N_y-1} \sum_{n_h=0}^{N_h-1}
\Nm {\M{Q} \DB {n_y, n_h}} ^4
\Nm {\V{u} \DB{n_h}} ^4 \NR
\NC =\NC N_Y^2 \D 4 N_Y ^{-4} \D \VNm {\V{u}} _4 ^4 \NR
\NC \leq \NC 4 N_Y ^{-2} \VNm {\V{u}} _2 ^4 \NR[+]
}
Now we have to bound \m {\i_{1,1} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,2}^2} and \m {\i_{2} \SB {\Fl {n_y/N_Y}, \Fl {n_y'/N_Y}} M_{B,4}} by \m {M_{B,4}} to simplifying matters, and similar for \m {E_3} and \m {E_4}.
\Disp {
\NC E_2
= \NC \sum _{\Stack { n_y, n_y' =0 \NR n_y <n_y' }}^{N_y-1}
\sum _{n_h =0}^{N_h-1}
\Nm {\M{Q} \DB {n_y, n_h}} ^2
\Nm {\M{Q} \DB {n_y', n_h}} ^2
\Nm {\V{u} \DB{n_h}} ^4 \NR
\NC = \NC N_Y \D \F{1}{2} N_Y \RB{N_Y-1} \D 4 N_Y ^{-4} \VNm {\V{u}} _2 ^4 \NR
\NC \NC \Q \Q + \F{1}{2} N_Y \RB{N_Y-1} \D N_Y^2 \D 4 N_R ^2 N_Y ^{-4} N_R ^{-4} \VNm {\V{u}} _2 ^4 \NR
\NC \leq \NC 4 \VNm {\V{u}} _2 ^4 \NR[+]
}
\Disp {
\NC E_3
=\NC \sum _{n_y, n_y' =0}^{N_y-1}
\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
\Nm {\M{Q} \DB {n_y, n_h}} ^2
\Nm {\M{Q} \DB {n_y', n_h'}} ^2
\Nm {\V{u} \DB{n_h}} ^2
\Nm {\V{u} \DB{n_h'}} ^2 \NR
\NC \leq \NC N_Y^2 \D \F{1}{2} N_H \RB{N_H-1} \D 4 N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC \leq \NC 4 N_Y ^{-1} \VNm {\V{u}} _2 ^4 \NR[+]
}
\Disp {
\NC E_4
=\NC \sum _{n_y =0}^{N_y-1}
\sum _{\Stack { n_h, n_h' =0 \NR n_h <n_h' }}^{N_h-1}
\Nm {\M{Q} \DB {n_y, n_h}} ^2
\Nm {\M{Q} \DB {n_y, n_h'}} ^2
\Nm {\V{u} \DB{n_h}} ^2
\Nm {\V{u} \DB{n_h'}} ^2 \NR
\NC \leq \NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D 4 N_Y ^{-4} \D \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR
\NC \leq \NC 4 N_H ^2 N_Y ^{-3} \VNm {\V{u}} _2 ^4 \NR[+]
}

The last one is more complicated.
We need a corollary that follows from ``Muirhead inequality''.
\Result
{Lemma}
{
If every component of \m {\V{u} \in \MB {M}_{\MB {C}} \SB {N_h}} is considered as a free variable taking complex values, then
\Disp {
\NC \NC \sum \i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'}
\V{u} \DB{n_h} \V{u} \DB{n_h'} \V{u} \DB{m_h} \V{u} \DB{m_h'} \NR
\NC \leq \NC \RB {1/6} \RB {\VNm {\V{u}} _2 ^4 -\VNm {\V{u}} _4 ^4} \NR[+]
}
}

Now,
\Disp {
\NC E_5
\NC = \sum _{
    \Stack {
      0 =n_h <n_h' \NR
      0 =m_h <m_h' \NR
      n_h +m_h' =n_h' +m_h \NR
      \Fl {n_h/N_H} =\Fl {n_h'/N_H} \NR
      \Fl {m_h/N_H} =\Fl {m_h'/N_H}
    }
  } ^{N_H-1}
  \sum _{\Stack { 0 =n_y <n_y' \NR \Fl {n_y/N_Y} =\Fl {n_y'/N_Y} }} ^{N_y-1} \NR
  \NC \NC \SixQ
  \M{Q} \DB {n_y, n_h}
  \M{Q} \DB {n_y, n_h'}
  \M{Q} \DB {n_y', m_h}
  \M{Q} \DB {n_y', m_h'} \NR
  \NC \NC \SixQ
  \V{u} \DB{n_h}
  \V{u} \DB{n_h'}
  \V{u} \DB{m_h}
  \V{u} \DB{m_h'} \NR
\NC =\NC N_Y \D \F{1}{2} N_H \RB{N_H-1} \D \F{1}{2} N_Y \RB{N_Y-1} \D N_H^2 \D 4 N_Y ^{-4} \NR
\NC \NC \SixQ
\D \sum_{n_h, n_h' =0} ^{N_H-1}
\sum_{m_h, m_h' =0} ^{N_H-1}
\i_{1,1,1,1} \SB {n_h, n_h', m_h, m_h'} \NR
\NC \NC \SixQ
\Nm {\V{u} \DB{n_h}}
\Nm {\V{u} \DB{n_h'}}
\Nm {\V{u} \DB{m_h}}
\Nm {\V{u} \DB{m_h'}} \NR
\NC \leq \NC \F{1}{3} N_Y ^{-1} N_H ^4 \VNm {\V{u}} _2 ^4. \NR[+]
}

@@

\Result
{Definition}
{
Consider \m {\V{x} \in \MB {V}_{\MB {K}} \SB {N_p}}.
Let bijection \m {\s: \MC {T} \SB {N_p} \mapsto \MC {T} \SB {N_p}} be defined to sort \m {\V{x}} in decreasing magnitude, meaning
\Disp{
\NC \V{v} \DB {\s \SB {n}}
\leq \NC \V{v} \DB {\s \SB {n-1}} \NR[+]
\NC n =\NC 1, \ldots, N_p-1 \NR
}
Its existence is evident.

@@

\Result
{Lemma}
{
\Disp {
\NC \Nm {\IP { \V {z} \SB {\o_z}, \M {P} \DB {:, n_g} }}
\leq \NC  2 \R {\log N_h} \NR
\NC n_g 
=\NC 1, \ldots, N_h. \NR
}
with probability \m {\geq 1 -N_h}.
}

@@

\Result
{Lemma}
{
With the condition that \m {\M {P}} satisfies RIP for \m {\d_s \SB {\M{P}}},
\Disp {
\NC \VNm {\M {P}^\Adj \M {P} \V {d}} _\infty
\leq \NC  4 \R {\log N_h} \NR
\NC n_g 
=\NC 1, \ldots, N_h. \NR
}
with probability \m {\geq 1 -N_h}.
}
